Legends for supplementary material

### 2019-05-12 Manuscript/Figures/figure_legends.Rmd
consolidated figure 4 into a table with bin and ir summaries; updated legends
updated legends

**Figure 4. Imbalance Ratios.** Boxplots illustrating the variations in imbalance ratios (IR) across cell line and resolution. IR was calculated by dividing the number of chromosome-specific genomic bins that overlapped with flanked TAD boundaries by the number of chromosome-specific genomic bins that did not.

@@

**Figure 6. Comparing category-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for GM12878.** Performances, separated by F1-Score and MCC, were compared for models using specific categories of annotations as the feature space including: histone modifications (red), chromatin state segmentations (green), transcription factor binding sites, and a feature space containing all 3 types combined (purple).

>>>>

@@

**Figure 6. Comparing annotation-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for GM12878.** MCC performances were compared for models using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple). Each bar represents a model ran through the ensemble framework, with re-sampling technique and predictor-type characteristics fixed to SMOTE and distance-types. The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.

### 2019-05-12 Manuscript/Supplementary/supplementary_legends.Rmd
updated legends

**Supplementary Figure 11. Comparing category-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for K562.** Performances, separated by F1-Score and MCC, were compared for models using specific categories of annotations as the feature space including: histone modifications (red), chromatin state segmentations (green), transcription factor binding sites, and a feature space containing all 3 types combined (purple).

>>>>

**Supplementary Figure 11.. Comparing annotation-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for K562.** MCC performances were compared for models using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple). Each bar represents a model ran through the ensemble framework, with re-sampling technique and predictor-type characteristics fixed to SMOTE and distance-types. The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.
